% !TEX root = main.tex
\documentclass[11pt]{article}

% ---------- Basics -----------
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{parskip}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{float}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue!60!black,
  citecolor=black
}

% ---------- Listings ----------
\lstset{
  basicstyle=\ttfamily\small,
  columns=fullflexible,
  breaklines=true,
  frame=single,
  framerule=0.2pt,
  tabsize=2,
  showstringspaces=false
}

% ---------- Title ----------
\newcommand{\product}{OpenBid}
\title{DIGT2107: Practice of Software Development\\
\Large Project Iteration 3.3: Final Project Submission\\[4pt]
\large \product{} -- Map-first Bidding Marketplace}
\author{Team 1: Tyler \and Mani \and Yanness \and Alaister}
\date{Due: March 29, 2026}

\begin{document}
\maketitle

\begin{center}
\textbf{Course:} DIGT2107 -- Winter Term 2026 \quad|\quad
\textbf{Instructor:} Dr.\ May Haidar
\end{center}

% =====================================================================
% 1. INTRODUCTION
% =====================================================================
\section{Introduction}

\textbf{Project Name:} \product \\
\textbf{Team Number:} 1 \\
\textbf{Team Members:} Tyler, Mani, Yanness, Alaister

\paragraph{Document Overview}
This document constitutes the final submission for Project Iteration 3.3 of the OpenBid
platform. It consolidates all required deliverable components into a single professional
artefact: the finalized Software Requirements Specification (SRS), the updated Software
Design Document (SDD), comprehensive Testing Documentation, and a complete User Manual.
The document reflects the system as it stands at the close of the project, incorporating
all changes, refinements, and expansions made throughout each development iteration.

\paragraph{Project Summary}
OpenBid is a map-first bidding marketplace that connects contractors (job posters) with
bidders (service providers). Users discover open jobs directly on an interactive Google
Maps interface, submit competitive proposals, communicate in real time, and transact
through a secure Stripe escrow payment system. The platform supports the complete job
lifecycle -- from discovery and bidding through award, payment, and post-job reviews --
and includes an administrative moderation dashboard for platform governance.

\paragraph{Technology Stack}
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{Frontend:} React 18, Vite, Google Maps JavaScript API, Stripe.js
  \item \textbf{Backend:} Node.js, Express, Socket.io
  \item \textbf{Database / Auth:} Firebase Firestore, Firebase Authentication
  \item \textbf{Payments / KYC:} Stripe Payments API, Stripe Identity
  \item \textbf{Two-Factor Authentication:} Duo Security (OIDC)
  \item \textbf{Testing:} Vitest + React Testing Library (client), Jest + Supertest (server)
  \item \textbf{Deployment:} Firebase Hosting, Google Cloud Run, Firebase Cloud Functions
\end{itemize}

\newpage

% =====================================================================
% 2. SOFTWARE REQUIREMENTS SPECIFICATION
% =====================================================================
\section{Software Requirements Specification}

\subsection{Overview}
This section presents the finalized Software Requirements Specification for the OpenBid
platform. It reflects all functional and non-functional requirements as they stand at
project completion, incorporating changes and additions made throughout the development
process. Requirements are organized by feature domain and cross-referenced to the team
members who led implementation of each area.

\subsection{Functional Requirements}

\subsubsection{User Authentication and Account Management}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-01 & The system shall allow users to register with an email address and password. & A new user account is created and a verification email is sent in production mode. \\
\midrule
FR-02 & The system shall block login until the user's email address is verified (production mode). & An unverified user receives a clear error message on login. \\
\midrule
FR-03 & The system shall allow users to log in with email and password and receive a session token. & A valid Firebase ID token is returned and stored in the client session on successful login. \\
\midrule
FR-04 & The system shall support optional two-factor authentication via Duo Security. & When Duo credentials are configured, users are redirected to a Duo OIDC challenge after password verification before a session is established. \\
\midrule
FR-05 & The system shall allow users to reset their password via an emailed link. & A password reset link is sent and allows the user to set a new password within 24 hours. \\
\midrule
FR-06 & The system shall allow authenticated users to switch between the \texttt{contractor} and \texttt{bidder} roles at any time. & Switching role immediately updates visible UI elements and API permissions without requiring a logout. \\
\bottomrule
\end{longtable}

\subsubsection{Job Posting and Discovery}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-07 & Contractors shall be able to post a job with a title, description, budget, and a map-pinned location. & The job appears on the map immediately after submission and is visible to all bidders. \\
\midrule
FR-08 & Bidders shall be able to discover open jobs by browsing the interactive map. & Clicking a job pin opens a job detail view. \\
\midrule
FR-09 & Contractors shall be able to edit or delete their own job postings. & Edits are reflected immediately; deletion removes the job and all associated bids from the platform. \\
\bottomrule
\end{longtable}

\subsubsection{Bidding}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-10 & Bidders shall be able to submit a bid on any open job they did not post. & Submitting a bid on a job posted by the same user returns an error. \\
\midrule
FR-11 & Contractors shall be able to view all bids received on their jobs and award one bid as the winner. & Awarding a bid closes the job to further bidding and notifies the awarded bidder. \\
\midrule
FR-12 & Bidders shall be able to view and manage all bids they have submitted via the My Bids page. & Bid status (pending, awarded, rejected) is displayed and updated in real time. \\
\bottomrule
\end{longtable}

\subsubsection{Payments and KYC}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-13 & The system shall create a Stripe PaymentIntent in manual capture mode when a bid is awarded, placing funds into escrow. & A payment record is stored in Firestore with status \texttt{held} and a valid Stripe PaymentIntent ID. \\
\midrule
FR-14 & The contractor shall be able to release escrow funds to the awarded bidder upon job completion. & Calling the release endpoint captures the PaymentIntent and updates the Firestore payment status to \texttt{released}. \\
\midrule
FR-15 & The system shall require KYC identity verification via Stripe Identity before a payment release can be completed. & Releasing payment without a verified KYC status returns an error with a redirect URL to the Stripe Identity session. \\
\midrule
FR-16 & KYC verification status shall be persisted on the user's profile and checked on each release attempt. & A verified user is not prompted to complete KYC again unless their verification has expired. \\
\midrule
FR-17 & All payment operations shall function in prototype mode without real Stripe credentials, using a mock adapter. & The Fund, Release, and Refund buttons complete successfully in prototype mode with simulated responses. \\
\midrule
FR-18 & Payment action buttons shall be visible only to the job's contractor and only in states where the action is valid. & The Fund button appears only before escrow is funded; the Release and Refund buttons appear only after funding; no buttons appear after release or refund. \\
\bottomrule
\end{longtable}

\subsubsection{Real-Time Messaging}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-19 & Users shall be able to send and receive text messages in real time without a page refresh. & A message sent by one user appears in the other user's conversation window within 500\,ms. \\
\midrule
FR-20 & Conversations shall be scoped to a specific job, keeping communication contextual. & Each conversation thread displays the associated job title and is inaccessible to users not party to that job. \\
\midrule
FR-21 & The message list shall automatically scroll to the most recent message when a new one arrives, with a scroll guard that respects the user's current position. & Auto-scroll triggers only when the user is within 100\,px of the bottom; reading older messages is not interrupted. \\
\midrule
FR-22 & Messages sent by the current user shall appear on the right; messages from others on the left. & CSS classes are applied based on sender UID comparison, providing clear visual distinction. \\
\midrule
FR-23 & Message history shall be persisted in Firestore and available on reconnect. & Reopening the messenger after a disconnect restores all previous messages in chronological order. \\
\midrule
FR-24 & Admin users shall be forbidden from accessing the messaging system. & A request to any messaging endpoint from an admin-role token returns HTTP 403. \\
\bottomrule
\end{longtable}

\subsubsection{Profile, Portfolio, and Reviews}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-25 & Users shall be able to upload and update a profile avatar image. & The new avatar is stored in Firebase Storage and displayed on the user's profile within one page reload. \\
\midrule
FR-26 & Users shall be able to view any other user's public profile, including bio, avatar, portfolio, and reviews. & The \texttt{/profile/:userId} route renders the target user's public information without requiring the viewer to be logged in. \\
\midrule
FR-27 & Users shall be able to add portfolio items, each consisting of an image, title, and description. & A submitted portfolio item appears on the user's profile immediately after submission. \\
\midrule
FR-28 & After a completed job, the contractor and the awarded bidder shall each be able to leave one review for the other. & Submitting a second review for the same job and person returns HTTP 409. \\
\midrule
FR-29 & Reviews shall include a star rating of 1 to 5 and a text comment, and the reviewee's average rating shall be recalculated after each new review. & The displayed average rating updates immediately after a review is submitted. \\
\bottomrule
\end{longtable}

\subsubsection{Admin Dashboard}

\begin{longtable}{@{}p{1.8cm}p{5.8cm}p{5.8cm}@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Acceptance Criteria} \\
\midrule
\endhead
FR-30 & The system shall provide an Admin Dashboard accessible only to users with the admin flag. & Navigating to \texttt{/admin} without admin privileges redirects to the home page. \\
\midrule
FR-31 & The Admin Dashboard shall display searchable, paginated lists of all users, jobs, and bids across three separate tabs. & Switching tabs updates the displayed content without a full page reload. \\
\midrule
FR-32 & Admins shall be able to edit any user, job, or bid via an inline editor modal that pre-populates all current values. & Changes submitted through the modal are immediately reflected in the table without a full reload. \\
\midrule
FR-33 & Admins shall be able to delete any user, job, or bid after confirming a deletion dialog. & The record is removed from the table within 300\,ms of confirmation. \\
\midrule
FR-34 & The system shall prevent admins from deleting their own account through the dashboard. & Attempting to delete the currently authenticated admin account returns an error. \\
\midrule
FR-35 & Client-side route guards shall prevent non-admin and unauthenticated users from accessing admin routes. & The \texttt{AdminRoute} wrapper component redirects these users to the home or login page. \\
\bottomrule
\end{longtable}

\subsection{Non-Functional Requirements}

\begin{longtable}{@{}p{3cm}p{10.5cm}@{}}
\toprule
\textbf{Category} & \textbf{Requirement} \\
\midrule
\endhead
Security & All routes that create, modify, or delete data require a valid Firebase ID token. Stripe operations use server-side secret keys exclusively. \\
\midrule
Prototype Mode & The full application shall run without any external service credentials by switching all adapters to their mock implementations via the \texttt{PROTOTYPE=TRUE} environment flag. \\
\midrule
Testability & Every server-side route module shall have a corresponding mock-mode test suite. Integration tests shall use the Firebase local emulator suite. \\
\midrule
Usability & The UI shall be responsive and fully functional on screens 360\,px wide and above. \\
\midrule
Data Integrity & Destructive admin operations require explicit user confirmation dialogs before execution. \\
\midrule
Availability & Prototype mode must allow full application functionality for demonstration and development without any live service dependency. \\
\bottomrule
\end{longtable}

\newpage

% =====================================================================
% 3. SOFTWARE DESIGN DOCUMENT
% =====================================================================
\section{Software Design Document}

\subsection{Architectural Overview}

OpenBid follows a layered client-server architecture with a strict separation between
the React single-page application, the Express REST and Socket.io server, and the
Firebase and Stripe backend services. The central architectural principle is the
\textbf{adapter pattern}: every external dependency (database, authentication, payments,
KYC, storage) has two interchangeable implementations -- a \texttt{*.real.js} file that
communicates with live services and a \texttt{*.mock.js} file used in prototype mode and
testing. The active implementation is selected at startup from the \texttt{PROTOTYPE}
environment variable, enabling the entire system to operate without external credentials.

\begin{figure}[H]
\centering
\begin{tabular}{|c|}
\hline
\\
\textbf{React Client} (Vite, React 18) \\
Pages \quad Components \quad Hooks \quad Services \\
\\
\hline
$\downarrow\uparrow$ \quad HTTP REST \quad $\downarrow\uparrow$ \quad WebSocket (Socket.io) \\
\hline
\\
\textbf{Express Server} \\
Routes \quad Middleware (RBAC) \quad Socket.io \\
\\
\hline
$\downarrow\uparrow$ \quad Adapter Layer \\
\hline
\textbf{Firebase Firestore \& Auth} \quad \textbf{Stripe Payments \& Identity} \quad \textbf{Duo Security} \\
\hline
\end{tabular}
\caption{High-Level System Architecture}
\end{figure}

\subsection{Role and Access Control Model}

Every authenticated user holds one of two operational roles -- \texttt{contractor} or
\texttt{bidder} -- and may switch freely between them. A separate boolean \texttt{isAdmin}
flag grants elevated platform privileges. Role is stored on the Firestore user document
and embedded in the session context so that both client-side route guards and server-side
middleware can enforce it independently.

\paragraph{Server-Side Enforcement}
The \texttt{requireRole.js} middleware provides two exported functions:
\texttt{requireRole(...allowedRoles)}, which permits only listed roles through, and
\texttt{forbidRole(...blockedRoles)}, which blocks listed roles regardless of other
permissions. These are composed on individual routes. The messaging system, for example,
uses \texttt{forbidRole("admin")} to prevent administrators from participating in user
conversations.

\paragraph{Client-Side Enforcement}
Two React wrapper components enforce access at the routing layer. \texttt{AdminRoute}
redirects any user who is unauthenticated or lacks the admin flag to the home page.
\texttt{NonAdminRoute} can redirect admin users away from standard user flows where
appropriate. Both components read from the shared \texttt{useAuth} context hook, which
is populated synchronously from cached session state to eliminate any flash of
protected content.

\subsection{Authentication and Session Management}

Firebase Authentication issues ID tokens on successful login. The Express server
validates these tokens on every protected request using the Firebase Admin SDK. The
validated UID is attached to the request object and used for all subsequent
authorization checks and database queries.

When Duo Security is enabled, the authentication flow includes an additional OIDC
redirect after password verification. The server initiates the Duo authorization
request, the user completes the Duo push or passcode challenge, and Duo's callback
exchanges an authorization code for a confirmation token. Only after this exchange is
the Firebase session fully established.

\subsection{Payment System Design}

The payment system implements a three-state escrow model using Stripe PaymentIntents
in manual capture mode.

\paragraph{State Machine}
\begin{center}
\texttt{[unfunded]} $\xrightarrow{\text{contractor funds}}$ \texttt{held}
$\xrightarrow{\text{job complete}}$ \texttt{released}\\[4pt]
\texttt{held} $\xrightarrow{\text{job cancelled}}$ \texttt{refunded}
\end{center}

State transitions are guarded server-side: only the contractor who created the job
may trigger a release or refund, enforced by comparing the authenticated UID against
the job's \texttt{contractorId} field before any Stripe API call is made.

\paragraph{KYC Gate}
Before executing a payment release, the server checks the \texttt{kycVerified} flag
on the user's Firestore document. If unverified, the server creates a Stripe Identity
\texttt{VerificationSession} and returns the session URL. When the user completes the
identity flow, Stripe sends a signed webhook event that the server uses to update
\texttt{kycVerified = true}. The release can then proceed on the user's next attempt.

\paragraph{Client-Side Button Visibility}

Payment button visibility is computed from a single \texttt{paymentStatus} value
fetched from the server when the Job Detail page loads. A mapping function translates
the status to the set of currently valid actions, keeping the JSX declarative and
independently testable.

\subsection{Real-Time Messaging Design}

The messaging system uses Socket.io for bidirectional real-time communication.
Conversations are keyed by a canonical room ID derived from the job ID and the
two participant UIDs (lexicographically sorted to ensure a single unique key per pair).
When a client connects, it emits a \texttt{join} event; the server joins the socket
to the appropriate room. All subsequent \texttt{sendMessage} events are emitted to the
full room (including the sender's socket), ensuring both participants see messages
without duplication.

Messages are simultaneously persisted to Firestore, providing a durable history that
is loaded on reconnection. The client-side scroll guard tracks the user's scroll
position and only auto-scrolls to new messages when the user is already within
100\,px of the bottom of the conversation, preserving reading position when browsing
history.

\subsection{Admin Dashboard Design}

The Admin Dashboard is a tabbed single-page component. Each tab -- Users, Jobs, Bids
-- is an independent child component that fetches its data on mount and maintains its
own local search and pagination state. The active tab is stored in the URL query
string (\texttt{?tab=users}) so that the browser's history stack preserves tab
state across navigation.

Entity editing is handled by a single reusable \texttt{EditorModal} component that
accepts the target entity, a field schema descriptor, and save/close callbacks. The
field schema drives dynamic form generation, allowing the same modal to serve all three
entity types without duplicated layout code.

\subsection{Profile, Portfolio, and Reviews Design}

User profiles aggregate data from three Firestore sources: the core user document (bio,
avatar URL, KYC status), a \texttt{portfolio} sub-collection, and a \texttt{reviews}
collection filtered by \texttt{revieweeId}. The profile page fetches all three in
parallel and displays a computed average star rating derived from the review collection.

Portfolio image uploads and avatar uploads both follow a two-step flow: the client
POSTs the file to the \texttt{/upload} route, the server validates the MIME type and
file size via Multer middleware, stores the file in Firebase Storage, and returns the
public URL. The client then PATCHes the relevant record with the new URL.

\subsection{System Component Summary}

\begin{longtable}{@{}p{0.28\linewidth} p{0.12\linewidth} p{0.18\linewidth} p{0.38\linewidth}@{}}
\toprule
\textbf{Component} & \textbf{Type} & \textbf{Technology} & \textbf{Responsibility} \\
\midrule
\endhead
\texttt{AdminDashboard.jsx} & Page & React & Tabbed admin interface: users, jobs, bids \\
\texttt{AdminRoute.jsx} & Component & React & Client-side admin route guard \\
\texttt{NonAdminRoute.jsx} & Component & React & Client-side non-admin route guard \\
\texttt{Messenger.jsx} & Page & React, Socket.io & Real-time chat UI with scroll guard \\
\texttt{Payment.jsx} & Page & React, Stripe.js & Escrow funding via Stripe Elements \\
\texttt{Profile.jsx} & Page & React & User profile with avatar, portfolio, reviews \\
\texttt{UserPortfolio.jsx} & Page & React & Portfolio management and display \\
\texttt{UserReviews.jsx} & Page & React & Review submission and listing \\
\texttt{MapView.jsx} & Component & Google Maps API & Job pin display and interaction \\
\texttt{admin.routes.js} & Router & Express & Admin CRUD for users, jobs, bids \\
\texttt{payments.routes.js} & Router & Express, Stripe & Escrow create, release, refund \\
\texttt{kyc.routes.js} & Router & Express, Stripe Identity & KYC session creation and webhook \\
\texttt{messages.routes.js} & Router & Express, Socket.io & Conversation and message management \\
\texttt{auth.routes.js} & Router & Express, Firebase & Login, signup, Duo 2FA \\
\texttt{reviews.routes.js} & Router & Express & Review CRUD and aggregation \\
\texttt{portfolio.routes.js} & Router & Express & Portfolio item CRUD \\
\texttt{upload.routes.js} & Router & Express, Multer & Avatar and photo upload handling \\
\texttt{requireRole.js} & Middleware & Express & Server-side RBAC enforcement \\
\texttt{payments.real.js} & Adapter & Stripe SDK & Production payment integration \\
\texttt{payments.mock.js} & Adapter & In-memory & Prototype mode payment simulation \\
\texttt{kyc.real.js} & Adapter & Stripe Identity SDK & Production KYC integration \\
\texttt{kyc.mock.js} & Adapter & In-memory & Prototype mode KYC simulation \\
\texttt{db.real.js} & Adapter & Firebase Firestore & Production data persistence \\
\texttt{db.mock.js} & Adapter & In-memory & Prototype mode data simulation \\
\texttt{auth.real.js} & Adapter & Firebase Auth & Production authentication \\
\texttt{auth.mock.js} & Adapter & In-memory & Prototype mode auth simulation \\
\bottomrule
\end{longtable}

\newpage

% =====================================================================
% 4. TESTING DOCUMENTATION
% =====================================================================
\section{Testing Documentation}

\subsection{Testing Methodology}

The project employs a two-layer testing strategy designed to provide confidence at
both the unit and integration levels while maintaining fast, reliable test execution
without mandatory dependencies on live external services.

\paragraph{Server-Side Testing}
Server-side tests are written with Jest and Supertest. Each route module has a
\textbf{mock-mode} test suite that substitutes all external adapters (database,
authentication, payments, KYC) with in-memory implementations. Where the system
behavior depends on real Firebase or Stripe interactions, separate
\textbf{integration tests} run against the Firebase local emulator suite in CI.

\paragraph{Client-Side Testing}
Client-side tests are written with Vitest and React Testing Library. Components are
rendered in a simulated DOM with mocked API services and context providers, testing
user-facing behaviour without a running backend.

\paragraph{Smoke Tests}
A dedicated smoke test suite validates critical-path behaviour when the application
runs with \texttt{PROTOTYPE=FALSE}, confirming that the real Firebase and Stripe
adapters initialise and respond correctly. These tests are designed to run quickly
as a pre-deployment gate.

\paragraph{Test Execution}
\begin{lstlisting}[language=bash]
# Run server-side tests
cd server && npm test

# Run client-side tests
cd client && npm test
\end{lstlisting}

\subsection{Test Suites and Coverage}

\subsubsection{Authentication Tests}

\paragraph{Files}
\texttt{auth.integration.real.routes.test.js}, \texttt{auth.duo.test.js}

\paragraph{Coverage}
\begin{itemize}[leftmargin=1.4em]
  \item Sign-up with valid credentials creates a user and returns a Firebase ID token.
  \item Login with correct credentials returns a valid session token.
  \item Login with an incorrect password returns HTTP 401.
  \item All protected routes return HTTP 401 when called without a token.
  \item All protected routes return HTTP 401 when called with a malformed or expired token.
  \item Duo 2FA callback: a valid authorization code completes the session; an invalid or replayed code returns HTTP 403.
  \item Password reset: requesting a reset for a registered email dispatches a reset link; requesting for an unknown email returns a safe, non-enumerable response.
\end{itemize}

\subsubsection{Payment System Tests}

\paragraph{Files}
\texttt{payments.routes.test.js}

\paragraph{Coverage}
The payment test suite contains 30 test cases covering the full escrow lifecycle:
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{Escrow creation:} Returns HTTP 201 with a \texttt{clientSecret} for a valid bid award; returns HTTP 400 for missing required fields; returns HTTP 409 when a payment already exists for the job.
  \item \textbf{Payment confirmation:} Transitions job status to \texttt{in\_progress}; prevents confirmation by non-contractors.
  \item \textbf{Payment release:} Captures the Stripe PaymentIntent and updates status to \texttt{released} for a KYC-verified contractor; returns HTTP 403 with a \texttt{kycUrl} for unverified users; returns HTTP 403 for non-contractors.
  \item \textbf{Refund:} Cancels or refunds the PaymentIntent and sets status to \texttt{refunded}; returns HTTP 404 for unknown payment IDs.
  \item \textbf{Status query:} Both the contractor and awarded bidder can view payment status; all other users receive HTTP 403.
  \item \textbf{Webhook handling:} A correctly-signed \texttt{payment\_intent.succeeded} event updates the Firestore payment record; unsigned or tampered webhooks return HTTP 400.
\end{itemize}

\subsubsection{KYC Tests}

\paragraph{Files}
\texttt{kyc.mock.routes.test.js}, \texttt{kyc.real.routes.test.js}

\paragraph{Coverage}
\begin{itemize}[leftmargin=1.4em]
  \item Mock mode: \texttt{POST /kyc/session} returns a synthetic session URL; the webhook endpoint sets \texttt{kycVerified = true} on the mock user document.
  \item Real mode (emulator): session creation returns a well-formed Stripe Identity URL; the webhook handler correctly processes a test verification event.
  \item Unauthenticated requests to KYC endpoints return HTTP 401.
\end{itemize}

\subsubsection{Jobs and Bids Integration Tests}

\paragraph{Files}
\texttt{jobs.integration.real.routes.test.js}, \texttt{bids.integration.real.routes.test.js}

\paragraph{Coverage}
\begin{itemize}[leftmargin=1.4em]
  \item Full lifecycle test: create job → submit bid → award bid → verify payment record is created in Firestore.
  \item Bidding on a job you own returns HTTP 403.
  \item Awarding a bid on another user's job returns HTTP 403.
  \item Listing jobs returns only open jobs by default; awarded and closed jobs appear with the correct filter.
  \item Editing a job you do not own returns HTTP 403.
  \item Deleting a job removes all associated bids.
\end{itemize}

\subsubsection{Admin Route Tests}

\paragraph{Files}
\texttt{admin.mock.routes.test.js}, \texttt{admin.real.routes.test.js}

\paragraph{Coverage -- 19 test cases}
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{GET /admin/users, /admin/jobs, /admin/bids:} Returns complete lists; returns HTTP 401 without authentication; returns HTTP 403 for non-admin authenticated users.
  \item \textbf{PATCH /admin/users/:id:} Returns HTTP 200 with the updated entity; returns HTTP 400 for an invalid email address format.
  \item \textbf{DELETE /admin/users/:id:} Returns HTTP 204; a subsequent GET confirms the record is absent; attempting to delete the authenticated admin's own account returns HTTP 400.
  \item \textbf{Response formatting:} User listings exclude sensitive fields such as password hashes; bid listings are returned in descending chronological order.
  \item Real-mode tests confirm that mutations are actually applied to the Firebase emulator, not just mocked.
\end{itemize}

\subsubsection{Messaging Tests}

\paragraph{Files}
\texttt{messages.mock.routes.test.js}, \texttt{messages.integration.real.routes.test.js}

\paragraph{Coverage -- 29 unit tests (mock) + integration tests}
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{Conversation creation:} A conversation is created when a bid is placed; duplicate creation for the same pair is idempotent.
  \item \textbf{Listing conversations:} Returns only conversations the authenticated user participates in; unauthenticated requests return HTTP 401.
  \item \textbf{Message sending:} Returns HTTP 200 with the stored message object; HTTP 400 for an empty message body; HTTP 403 for non-participant senders.
  \item \textbf{Message history:} Retrieved in chronological order; read markers update correctly; non-participants receive HTTP 403 or 404.
  \item \textbf{Hide / Unhide / Delete:} Hide removes the conversation from the default listing; unhide restores it; delete permanently removes it; only participants may perform these actions.
  \item \textbf{Admin restriction:} Any messaging endpoint accessed with an admin token returns HTTP 403.
  \item \textbf{Integration:} Two emulator users exchange messages; history is verified on reconnect; messages in one room do not appear in another room.
\end{itemize}

\subsubsection{Reviews Tests}

\paragraph{Files}
\texttt{reviews.routes.test.js}

\paragraph{Coverage -- 7 test cases}
\begin{itemize}[leftmargin=1.4em]
  \item A review can only be submitted after the job has been awarded, and only for the awarded provider -- attempts before award or for the wrong user are rejected.
  \item Users cannot review themselves; users not party to the job cannot submit a review.
  \item Duplicate review submissions (same reviewer, same job, same reviewee) return HTTP 409.
  \item Review photos upload correctly and appear in the user's review list with thumbnail links.
  \item Only the review author can edit the review; the rating and text can be updated independently; clearing the description does not invalidate the review.
  \item Review listing returns records in reverse-chronological order; the computed average rating reflects all submitted reviews.
\end{itemize}

\subsubsection{Upload Tests}

\paragraph{Files}
\texttt{upload.avatar.routes.test.js}

\paragraph{Coverage}
\begin{itemize}[leftmargin=1.4em]
  \item A valid JPEG or PNG upload returns HTTP 200 with a public storage URL in the response body.
  \item Uploading a file with an unsupported MIME type (e.g.\ \texttt{application/pdf}) returns HTTP 400.
  \item A request with no file attached returns HTTP 400 with a descriptive error message.
  \item A file exceeding the configured size limit returns HTTP 413.
\end{itemize}

\subsubsection{Client-Side Component Tests}

\paragraph{Admin Dashboard Tests} \texttt{(AdminDashboard.test.jsx)}
\begin{itemize}[leftmargin=1.4em]
  \item The component renders without crashing when supplied with mock user, job, and bid data.
  \item Clicking a tab header updates the visible content pane to the correct section.
  \item Opening the editor for a record pre-populates the email field with the record's current value.
  \item Clicking the delete button surfaces a confirmation dialog before dispatching any delete action.
\end{itemize}

\paragraph{Navigation and Session Tests} \texttt{(nav.test.jsx, session.test.js)}
\begin{itemize}[leftmargin=1.4em]
  \item The \texttt{Nav} component displays the correct role label for the user's active role.
  \item The admin dashboard link is visible only when \texttt{isAdmin} is \texttt{true}.
  \item Clicking the role switch button invokes the role change handler exactly once.
  \item The \texttt{useSession} hook reads the active role from \texttt{localStorage} on mount; calling \texttt{switchRole} writes the new role and updates the context; clearing storage and re-mounting defaults to the server-supplied role.
\end{itemize}

\paragraph{Messenger and Socket Tests} \texttt{(Messenger.test.jsx, socket.test.js)}
\begin{itemize}[leftmargin=1.4em]
  \item The Messenger page renders an empty-state placeholder when no conversation is selected.
  \item Messages from the current user carry the \texttt{.message--sent} CSS class; messages from others carry \texttt{.message--received}.
  \item When a new message arrives and \texttt{nearBottom} is \texttt{true}, the container scrolls to the bottom; when \texttt{nearBottom} is \texttt{false}, the scroll position is unchanged.
  \item The socket service returns the same singleton instance across multiple calls to \texttt{getSocket}.
  \item \texttt{connectSocket} and \texttt{disconnectSocket} correctly manage the connection lifecycle.
  \item Event subscriptions via \texttt{onNewMessage} can be unsubscribed without leaking listeners.
\end{itemize}

\paragraph{Profile Tests} \texttt{(Profile.test.jsx)}
\begin{itemize}[leftmargin=1.4em]
  \item The Profile component renders the user's name and bio from mock data.
  \item Portfolio items are displayed as a grid; an empty portfolio shows a placeholder message.
  \item The average star rating is computed and rendered correctly from mock review data.
  \item The review submission form is not rendered when the viewer is viewing their own profile.
\end{itemize}

\paragraph{Map Utility Tests} \texttt{(mapHelpers.test.js, locationHelpers.test.js)}
\begin{itemize}[leftmargin=1.4em]
  \item \texttt{formatCoordinate} rounds latitude and longitude values to four decimal places.
  \item \texttt{isWithinBounds} correctly classifies coordinates inside and outside a given bounding box, including coordinates exactly on the boundary.
  \item \texttt{calculateDistance} returns the correct Haversine distance within a 1\% tolerance for known city coordinate pairs, including the edge case of zero distance.
  \item \texttt{parseGeoPoint} converts a Firestore GeoPoint into a plain \texttt{\{lat, lng\}} object.
\end{itemize}

\subsection{Test Results Summary}

\begin{longtable}{@{}p{0.32\linewidth} p{0.12\linewidth} p{0.12\linewidth} p{0.38\linewidth}@{}}
\toprule
\textbf{Test Suite} & \textbf{Tests} & \textbf{Status} & \textbf{Notes} \\
\midrule
\endhead
auth routes (real)          & 8  & Pass & Firebase emulator \\
auth.duo                    & 4  & Pass & Mock Duo OIDC \\
payments routes             & 30 & Pass & Mock adapter \\
kyc routes (mock)           & 6  & Pass & Mock adapter \\
kyc routes (real)           & 4  & Pass & Firebase emulator \\
jobs integration (real)     & 9  & Pass & Firebase emulator \\
bids integration (real)     & 7  & Pass & Firebase emulator \\
admin routes (mock)         & 11 & Pass & Mock adapter \\
admin routes (real)         & 8  & Pass & Firebase emulator \\
messages routes (mock)      & 29 & Pass & Mock adapter \\
messages integration (real) & 6  & Pass & Firebase emulator \\
reviews routes              & 7  & Pass & Mock adapter \\
upload avatar routes        & 5  & Pass & Mock storage \\
AdminDashboard component    & 4  & Pass & Vitest + RTL \\
nav component               & 4  & Pass & Vitest + RTL \\
session hook                & 3  & Pass & Vitest \\
Messenger component         & 6  & Pass & Vitest + RTL \\
socket service              & 7  & Pass & Vitest \\
Profile component           & 4  & Pass & Vitest + RTL \\
mapHelpers                  & 5  & Pass & Vitest \\
locationHelpers             & 3  & Pass & Vitest \\
\midrule
\textbf{Total}              & \textbf{170} & \textbf{All Pass} & \\
\bottomrule
\end{longtable}

\newpage

% =====================================================================
% 5. USER MANUAL
% =====================================================================
\section{User Manual}

\subsection{Introduction}

\textbf{Purpose:}
OpenBid is a map-first bidding marketplace that connects contractors -- individuals or
businesses seeking to have work done -- with bidders who offer their services. The
platform enables job discovery through an interactive map, competitive bidding,
secure escrow payments, real-time messaging, and post-job reviews.

\textbf{Target Audience:}
Any individual or business seeking to post work or offer professional services on a
location-aware platform.

\textbf{Key Features:}
\begin{itemize}[leftmargin=1.4em]
  \item Visual job discovery on Google Maps
  \item Competitive bidding and bid management workflow
  \item Secure Stripe escrow payments with KYC verification
  \item Real-time in-app messaging between contractors and bidders
  \item Two-factor authentication via Duo Security
  \item User portfolios and post-job review system
  \item Administrative moderation dashboard
\end{itemize}

\subsection{Installation and Setup}

\subsubsection{Prerequisites}
\begin{itemize}[leftmargin=1.4em]
  \item Node.js v16 or higher
  \item npm v8 or higher
  \item Git
\end{itemize}

\subsubsection{Quick Start -- Prototype Mode (No External Services Required)}

Prototype mode requires no API keys or external accounts. All data is held in memory
and resets when the server restarts.

\begin{lstlisting}[language=bash]
# 1. Clone the repository
git clone <repository-url>
cd OpenBid-Map-first-Bidding-Markplace

# 2. Install server dependencies
cd server && npm install

# 3. Install client dependencies
cd ../client && npm install

# 4. Start the backend (prototype mode is the default)
cd ../server
npm run dev

# 5. In a separate terminal, start the frontend
cd ../client
npm run dev
\end{lstlisting}

Open \texttt{http://localhost:5173} in your browser.

\textbf{Default Admin Credentials (Prototype Mode):}
\begin{itemize}[leftmargin=1.4em]
  \item Email: \texttt{openbidadmin@gmail.com}
  \item Password: \texttt{adminiamadmin}
\end{itemize}

\subsubsection{Production Mode -- Firebase and Stripe}

For full functionality with persistent data, email verification, KYC, and payments,
create the following environment files before starting the application.

\textbf{server/.env}
\begin{lstlisting}
PROTOTYPE=FALSE
PORT=4000
FIREBASE_PROJECT_ID=<your_project_id>
FIREBASE_CLIENT_EMAIL=<your_client_email>
FIREBASE_PRIVATE_KEY="-----BEGIN PRIVATE KEY-----\n...\n-----END PRIVATE KEY-----\n"
FIREBASE_WEB_API_KEY=<your_firebase_web_api_key>
FIREBASE_STORAGE_BUCKET=<your_storage_bucket>
STRIPE_SECRET_KEY_FOR_TESTING=sk_test_<your_stripe_secret_key>
STRIPE_PUBLISHABLE_KEY=pk_test_<your_stripe_publishable_key>
STRIPE_WEBHOOK_SECRET=whsec_<your_webhook_secret>
APP_URL=http://localhost:5173
EMAIL_VERIFICATION_REDIRECT=http://localhost:5173/login
# Optional: Duo 2FA
DUO_CLIENT_ID=
DUO_CLIENT_SECRET=
DUO_API_HOST=
DUO_REDIRECT_URI=
\end{lstlisting}

\textbf{client/.env}
\begin{lstlisting}
VITE_PROTOTYPE=FALSE
VITE_API_BASE=http://localhost:4000
VITE_GOOGLE_MAPS_API_KEY=<your_google_maps_api_key>
VITE_STRIPE_PUBLISHABLE_KEY=<your_stripe_publishable_key>
\end{lstlisting}

\subsubsection{Running Tests}
\begin{lstlisting}[language=bash]
cd server && npm test    # Server-side tests
cd client && npm test    # Client-side tests
\end{lstlisting}

\subsection{User Interface Guide}

\subsubsection{Navigation Bar}
The navigation bar appears at the top of every page and provides access to all
primary sections of the application. The active role (Contractor or Bidder) is
displayed prominently and can be changed with the role switch toggle. Admin users
see an additional \textbf{Admin Dashboard} link.

\subsubsection{Map View (Home Page)}
The home page displays an interactive Google Maps view with pins representing all
open jobs. Clicking any pin opens a popup with the job title, budget, and a link to
the full job detail page. The search bar above the map filters visible pins in real
time by keyword or location.

\subsubsection{Job Detail Page}
The job detail page shows the full job description, posted date, budget, and all
bids received. Contractors see their own job's bid list and payment action buttons.
Bidders see an option to place a bid on jobs they have not yet bid on.

\subsubsection{Messenger Page}
The Messenger page is divided into a conversation list on the left and an active
chat pane on the right. Messages are delivered instantly without refreshing. Selecting
a different conversation switches the chat pane.

\subsubsection{Profile Page}
A user's profile page displays their avatar, bio, portfolio gallery, and a list of
reviews received from past jobs. From your own profile, you can edit your bio, upload
an avatar, and manage portfolio items.

\subsection{Core Features Guide}

\subsubsection{Creating an Account}
\begin{enumerate}[leftmargin=1.8em]
  \item Navigate to the application and click \textbf{Sign Up}.
  \item Enter your full name, email address, and a password of at least six characters.
  \item In production mode, check your inbox and click the verification link before logging in. In prototype mode, you can log in immediately.
  \item Choose an initial role: \textbf{Contractor} to post jobs or \textbf{Bidder} to apply for jobs.
\end{enumerate}

\subsubsection{Logging In and Two-Factor Authentication}
\begin{enumerate}[leftmargin=1.8em]
  \item Enter your email and password on the Login page and click \textbf{Log In}.
  \item If Duo Security 2FA is enabled on the system, you will be redirected to complete a Duo push notification or enter a passcode.
  \item After successful authentication, you are taken to the main job map.
\end{enumerate}

\subsubsection{Switching Roles}
Click the role indicator in the navigation bar and select the role you wish to switch to. The interface updates immediately to reflect the new role's available actions.

\subsubsection{Posting a Job (Contractor)}
\begin{enumerate}[leftmargin=1.8em]
  \item Ensure your active role is set to \textbf{Contractor}.
  \item Click \textbf{Post Job} in the navigation bar.
  \item Enter a job title, full description, and your budget.
  \item Click on the map to set the job's location pin.
  \item Click \textbf{Submit}. The job will appear on the map immediately.
\end{enumerate}

\subsubsection{Finding and Bidding on Jobs (Bidder)}
\begin{enumerate}[leftmargin=1.8em]
  \item Ensure your active role is set to \textbf{Bidder}.
  \item Browse the map for job pins or use the search bar to filter by keyword or location.
  \item Click a pin and then \textbf{View Job} to open the job detail page.
  \item Click \textbf{Place Bid}, enter your proposed amount and a cover message, then click \textbf{Submit Bid}.
  \item You can monitor all your submitted bids from the \textbf{My Bids} page.
\end{enumerate}

\subsubsection{Awarding a Bid and Processing Payment (Contractor)}
\begin{enumerate}[leftmargin=1.8em]
  \item Open one of your job postings from the map or your jobs list.
  \item Review the bids received and click \textbf{Award Bid} next to your preferred bidder.
  \item You will be prompted to fund the escrow. Click \textbf{Fund Escrow} and complete the Stripe payment form.
  \item Once the job is complete, click \textbf{Release Payment} to transfer funds to the bidder. You may need to complete KYC identity verification before your first release.
  \item If the job is cancelled, click \textbf{Request Refund} to return the escrowed funds.
\end{enumerate}

\subsubsection{Messaging}
\begin{enumerate}[leftmargin=1.8em]
  \item Click the \textbf{Messages} icon in the navigation bar to open the Messenger page.
  \item Select an existing conversation from the list, or start a new conversation from a job or bid detail page.
  \item Type your message in the input field at the bottom and press Enter or click \textbf{Send}.
  \item Messages are delivered in real time. You do not need to refresh the page.
  \item To hide a conversation, hover over it in the list and click the hide option. To permanently delete it, use the delete option.
\end{enumerate}

\subsubsection{Managing Your Profile and Portfolio}
\begin{enumerate}[leftmargin=1.8em]
  \item Click your name or avatar in the navigation bar to open your profile.
  \item Click \textbf{Edit Profile} to update your bio.
  \item Click the avatar to upload a new profile picture (JPEG or PNG, up to 1\,MB).
  \item Under the \textbf{Portfolio} section, click \textbf{Add Item} to add a project showcase with an image, title, and description.
\end{enumerate}

\subsubsection{Leaving a Review}
\begin{enumerate}[leftmargin=1.8em]
  \item Navigate to a completed job. Both the contractor and the awarded bidder will see a \textbf{Leave a Review} option.
  \item Select a star rating from 1 to 5 and write an optional comment.
  \item Optionally attach a photo to the review.
  \item Submit. The review appears on the reviewee's public profile and their average rating is updated.
\end{enumerate}

\subsubsection{Using the Admin Dashboard}
\begin{enumerate}[leftmargin=1.8em]
  \item Log in with an admin account and click \textbf{Admin Dashboard} in the navigation bar, or navigate directly to \texttt{/admin}.
  \item Select the \textbf{Users}, \textbf{Jobs}, or \textbf{Bids} tab to browse the corresponding records.
  \item Use the search field at the top of each tab to filter records by keyword.
  \item Click the edit icon on any row to open the editor modal. Make changes and click \textbf{Save}.
  \item Click the delete icon and confirm the deletion dialog to permanently remove a record.
\end{enumerate}

\subsection{Troubleshooting and FAQs}

\begin{longtable}{@{}p{5.2cm}p{8.4cm}@{}}
\toprule
\textbf{Issue} & \textbf{Solution} \\
\midrule
\endhead
Cannot log in after sign-up & In production mode, check your inbox for the verification email and click the link before attempting to log in. Check your spam folder if it does not arrive within a minute. \\
\midrule
Map does not display any pins & Ensure \texttt{VITE\_GOOGLE\_MAPS\_API\_KEY} is set in \texttt{client/.env}. In prototype mode the map renders with limited tiles but pins will still display. \\
\midrule
Fund / Release / Refund button not visible & Payment buttons are visible only to the job's contractor. Ensure you are viewing a job you posted and that the job's current payment status matches the expected action (e.g.\ Release is only available after funding). \\
\midrule
Messages not delivering in real time & Confirm the server is running and that the WebSocket connection is not blocked by a firewall, proxy, or browser extension. Try refreshing the page to re-establish the socket connection. \\
\midrule
Two-factor authentication not appearing & Duo 2FA is optional and only active when the Duo environment variables are configured in \texttt{server/.env}. If they are absent, the login flow skips the second factor. \\
\midrule
All data disappears on server restart & This is expected behaviour in prototype mode. Data is held in memory only. Switch to \texttt{PROTOTYPE=FALSE} with a configured Firebase project for persistent storage. \\
\midrule
KYC verification stuck on ``pending'' & Stripe Identity verification can take a few minutes to process. Refresh your profile page after completing the identity flow. Ensure the Stripe webhook is correctly configured to point to your server's \texttt{/api/kyc/webhook} endpoint. \\
\midrule
Admin dashboard shows ``Unauthorised'' & Only accounts with the \texttt{isAdmin} flag set in Firestore can access \texttt{/admin}. In prototype mode, use the default admin credentials listed in the Quick Start section above. \\
\midrule
Portfolio image upload fails & Ensure the image is a JPEG or PNG and does not exceed 1\,MB. Images are automatically resized client-side, but very large or unusual formats may still fail validation. \\
\midrule
Review submission returns an error & Ensure the job has been awarded before attempting to leave a review. Each reviewer may submit only one review per job per person -- a second submission will be rejected. \\
\bottomrule
\end{longtable}

\end{document}
