% !TEX root = main.tex
\documentclass[11pt]{article}

% ---------- Basics -----------
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{parskip}
\usepackage{listings}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue!60!black,
  citecolor=black
}

% ---------- Listings ----------
\lstset{
  basicstyle=\ttfamily\small,
  columns=fullflexible,
  breaklines=true,
  frame=single,
  framerule=0.2pt,
  tabsize=2,
  showstringspaces=false
}

% ---------- Title ----------
\newcommand{\product}{OpenBid}
\title{DIGT2107: Practice of Software Development\\
\Large Project Iteration 3: Testing and Initial Development\\[4pt]
\large \product}
\author{Team 1: Tyler \and Mani \and Yanness \and Alaister}
\date{Due: November 2, 2025}

\begin{document}
\maketitle

\begin{center}
\textbf{Course:} DIGT2107 -- Fall Term 2025 \quad|\quad
\textbf{Instructor:} Dr.\ May Haidar
\end{center}

\tableofcontents
\newpage

% ===================== 1. Introduction =====================
\section{Introduction}
\textbf{Project Name:} \product \\
\textbf{Team Number:} \textbf{1} \\
\textbf{Team Members:} Tyler, Mani, Yanness, Alaister

\paragraph{Document Overview}
This document outlines the deliverables for Iteration 3, focusing on the initial development phase. It shows how our \textit{test cases} map to the \textit{functional and non-functional requirements} from earlier iterations, and it reports the current working prototype. Goals: implement core functionality tied to high-priority stories, develop comprehensive unit tests, and deliver a working prototype demonstrating traceability.

% ===================== 2. Iteration Goals and Objectives =====================
\section{Iteration Goals and Objectives}
\begin{itemize}[leftmargin=1.4em]
  \item Implement core flows: \textbf{auth + Duo 2FA}, \textbf{KYC gate} (stubbed via Stripe Identity sandbox token), \textbf{post a job}, \textbf{browse on map}, \textbf{place a bid}.
  \item Develop and run unit tests mapped to requirements (frontend component tests and backend handler tests).
  \item Deliver a prototype demonstrating requirement \(\leftrightarrow\) test case links.
\end{itemize}

% ===================== 3. Requirement to Test Case Traceability =====================
\section{Requirement to Test Case Traceability}
Tables below map each requirement to the test cases that validate it. Coverage status will be updated as testing completes.

\subsection*{Functional Requirements (FR)}
\begin{longtable}{@{}p{0.12\linewidth} p{0.55\linewidth} p{0.15\linewidth} p{0.14\linewidth}@{}}
\toprule
\textbf{Req ID} & \textbf{Requirement Description} & \textbf{Test Case IDs} & \textbf{Coverage} \\
\midrule
\endhead
FR-001 & System shall allow authenticated users to \textbf{post jobs} with title, description, budget, photos, and location. & TC-001, TC-002 & Partially Covered \\
FR-002 & System shall allow providers to \textbf{browse jobs on a map} with basic filters (radius, category). & TC-003, TC-004 & Partially Covered \\
FR-003 & System shall allow providers to \textbf{place bids} on open jobs; posters can view and accept a bid. & TC-005, TC-006 & Partially Covered \\
FR-004 & System shall enforce \textbf{KYC for all users} before posting or bidding. & TC-007 & Partially Covered \\
FR-005 & System shall support \textbf{user authentication} with \textbf{Duo 2FA} for sensitive actions. & TC-008 & Partially Covered \\
FR-006 & System shall provide \textbf{in-thread messaging} per job after acceptance. & TC-009 & Planned \\
FR-007 & System shall record \textbf{ratings and reviews} after job completion. & TC-010 & Planned \\
\bottomrule
\end{longtable}

\subsection*{Non-Functional Requirements (NFR)}
\begin{longtable}{@{}p{0.12\linewidth} p{0.55\linewidth} p{0.15\linewidth} p{0.14\linewidth}@{}}
\toprule
\textbf{Req ID} & \textbf{Requirement Description} & \textbf{Test Case IDs} & \textbf{Coverage} \\
\midrule
\endhead
NFR-001 & \textbf{Performance:} Search/browse should return results within 800\,ms P95 for a metro with 5k open jobs (stub data). & TC-011 & Planned \\
NFR-002 & \textbf{Security:} Only KYC-verified users can hit write endpoints for jobs/bids. & TC-007, TC-012 & Partially Covered \\
NFR-003 & \textbf{Usability:} Map view and list view maintain accessible contrast and keyboard navigation for core actions. & TC-013 & Planned \\
\bottomrule
\end{longtable}

\paragraph{Notes}
\begin{itemize}[leftmargin=1.4em]
  \item Each requirement is validated by one or more test cases. Gaps are flagged as \textit{Planned}.
  \item NFR coverage status is informative only (not required for grading), but we track it to guide future work.
\end{itemize}

% ===================== 4. Detailed Test Case Descriptions =====================
\section{Detailed Test Case Descriptions}
For brevity we include the highest-priority cases now; the full catalog will live in the repo under \texttt{tests/}.

\subsection*{TC-001}
\textbf{Title:} Post Job - Valid Inputs \\
\textbf{Requirement:} FR-001 \\
\textbf{Preconditions:} User is logged in, KYC status = verified. \\
\textbf{Steps:}
\begin{enumerate}[leftmargin=1.4em]
  \item Navigate to \texttt{/new-job}.
  \item Enter valid title, description, budget, and pick a map location (mocked Google Maps).
  \item Upload a photo (mock file).
  \item Click \texttt{Post}.
\end{enumerate}
\textbf{Expected Result:} Job document is created in Firestore; UI redirects to Job Detail. \\
\textbf{Actual Result:} To be filled after execution. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-002}
\textbf{Title:} Post Job - Validation Errors \\
\textbf{Requirement:} FR-001 \\
\textbf{Preconditions:} Logged in, KYC verified. \\
\textbf{Steps:}
\begin{enumerate}[leftmargin=1.4em]
  \item Navigate to \texttt{/new-job}.
  \item Leave title empty; click \texttt{Post}.
\end{enumerate}
\textbf{Expected Result:} Client-side validation shows error; no write occurs. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-003}
\textbf{Title:} Map Browse - Within Radius \\
\textbf{Requirement:} FR-002 \\
\textbf{Preconditions:} Seeded jobs exist within 10\,km. \\
\textbf{Steps:}
\begin{enumerate}[leftmargin=1.4em]
  \item Open \texttt{/jobs}.
  \item Set radius filter = 10\,km.
\end{enumerate}
\textbf{Expected Result:} Pins and list only include jobs within 10\,km. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-004}
\textbf{Title:} Map Browse - Category Filter \\
\textbf{Requirement:} FR-002 \\
\textbf{Expected Result:} Only jobs of selected category are shown. \\
\textbf{Status:} Pending \quad \textbf{Priority:} Medium

\subsection*{TC-005}
\textbf{Title:} Place Bid - Valid \\
\textbf{Requirement:} FR-003 \\
\textbf{Preconditions:} Provider is logged in, KYC verified, job is open. \\
\textbf{Expected Result:} Bid document created; poster sees bid in Job Detail. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-006}
\textbf{Title:} Accept Bid - Poster Flow \\
\textbf{Requirement:} FR-003 \\
\textbf{Expected Result:} Job status transitions to \texttt{awarded}; winning bid marked \texttt{accepted}. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-007}
\textbf{Title:} KYC Gate - Block Unverified Writes \\
\textbf{Requirement:} FR-004, NFR-002 \\
\textbf{Preconditions:} User KYC status = pending. \\
\textbf{Expected Result:} Attempts to post job or bid are rejected by Firestore rules/API; UI shows KYC required. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-008}
\textbf{Title:} Duo 2FA Challenge on Sensitive Action \\
\textbf{Requirement:} FR-005 \\
\textbf{Preconditions:} User logged in without recent 2FA; action = add payout method. \\
\textbf{Expected Result:} Duo prompt required; action proceeds only on success. \\
\textbf{Status:} Pending \quad \textbf{Priority:} Medium

\subsection*{TC-009}
\textbf{Title:} Messaging After Acceptance \\
\textbf{Requirement:} FR-006 \\
\textbf{Expected Result:} Parties can exchange messages in job thread; messages persist in Firestore. \\
\textbf{Status:} Planned \quad \textbf{Priority:} Medium

\subsection*{TC-010}
\textbf{Title:} Submit Review on Completion \\
\textbf{Requirement:} FR-007 \\
\textbf{Expected Result:} Review saved and visible on profile; duplicate review blocked. \\
\textbf{Status:} Planned \quad \textbf{Priority:} Medium

\subsection*{TC-011}
\textbf{Title:} Performance P95 - Map Query \\
\textbf{Requirement:} NFR-001 \\
\textbf{Expected Result:} P95 end-to-end from filter change to results render \(\leq 800\,\)ms on stub dataset. \\
\textbf{Status:} Planned \quad \textbf{Priority:} Low

\subsection*{TC-012}
\textbf{Title:} Ruleset Audit - No Write Without Claims \\
\textbf{Requirement:} NFR-002 \\
\textbf{Expected Result:} Firestore rules reject writes missing \texttt{kycVerified == true}. \\
\textbf{Status:} Pending \quad \textbf{Priority:} High

\subsection*{TC-013}
\textbf{Title:} Accessibility - Keyboard Nav on Map/List \\
\textbf{Requirement:} NFR-003 \\
\textbf{Expected Result:} Tabbing reaches filters, list items, and primary actions; visible focus outlines present. \\
\textbf{Status:} Planned \quad \textbf{Priority:} Low

% ===================== 5. Code Repository and Branching Strategy =====================
\section{Code Repository and Branching Strategy}
\textbf{Repository:} \url{https://github.com/your-org/openbid} \textit{(placeholder)} \\[4pt]
\textbf{Branches:}
\begin{itemize}[leftmargin=1.4em]
  \item \texttt{main}: stable releases.
  \item \texttt{develop}: ongoing integration.
  \item \texttt{feature/\{slug\}}: e.g., \texttt{feature/auth}, \texttt{feature/map}, \texttt{feature/bids}, \texttt{feature/kyc}, \texttt{feature/tests}.
\end{itemize}

% ===================== 6. Task Allocation and Timeline =====================
\section{Task Allocation and Timeline}
\textbf{Pair-Programming Rotation (weekly):} two pairs; driver/navigator swap daily; Scrum Master rotates weekly (Tyler \(\rightarrow\) Mani \(\rightarrow\) Yanness \(\rightarrow\) Alaister).

\subsection*{Sprint Plan (3 weeks for Iteration 3)}
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{Week 1:} Implement auth + Duo 2FA hook, KYC gate stub, Post Job UI/API, initial tests (TC-001, TC-002, TC-007, TC-008).
  \item \textbf{Week 2:} Map browse (pins, filters), Place Bid flow, tests (TC-003, TC-004, TC-005, TC-006, TC-012).
  \item \textbf{Week 3:} Prototype hardening, accessibility pass (keyboard focus), performance harness scaffolding, test documentation (TC-011, TC-013 planning).
\end{itemize}

\subsection*{Task Breakdown (examples)}
\begin{itemize}[leftmargin=1.4em]
  \item Frontend: NewJob form, MapView, JobList, Bid modal, validation.
  \item Backend (Express on Firebase Functions/Cloud Run): endpoints for jobs, bids; KYC/Duo middleware.
  \item Firestore rules: enforce \texttt{kycVerified == true} for job/bid writes.
  \item Testing: Vitest/Jest + React Testing Library for UI; supertest for API; rules-unit-testing for Firestore.
  \item Docs: update traceability, add test run notes.
\end{itemize}

% ===================== 7. Prototype Overview =====================
\section{Prototype Overview}
\textbf{Stack (MVP):} React + SCSS (Firebase Hosting), Node.js + Express (Firebase Functions or Cloud Run), Firestore, Google Maps JS, Stripe (Connect/Identity), Duo 2FA.

\subsection*{Implemented in Iteration 3 (target)}
\begin{itemize}[leftmargin=1.4em]
  \item Auth shell with Duo challenge on sensitive action.
  \item KYC gate (UI + rules) using a sandbox token flow.
  \item Post Job UI + server write; basic Job Detail.
  \item Map browse with radius/category filters on seeded data.
  \item Place Bid basic happy path.
\end{itemize}

% ===================== 8. Submission Guidelines =====================
\section{Submission Guidelines}
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{GitHub:} Push code and documentation; tag release as \texttt{ITR2.1}.
  \item \textbf{eClass PDF:} include \textit{Prototype Overview}, \textit{Updated Requirements/Use Cases}, \textit{Test Plan and (initial) Results}, and \textit{Updated Iteration Plan/Backlog}.
\end{itemize}

% ===================== Appendix A: Sample Test Skeletons =====================
\section*{Appendix A: Test Skeletons (illustrative)}
\subsection*{Frontend (React Testing Library)}
\begin{lstlisting}
import { render, screen, fireEvent } from '@testing-library/react'
import NewJob from '../src/pages/NewJob'

test('TC-002: shows validation error when title empty', async () => {
  render(<NewJob />)
  fireEvent.click(screen.getByRole('button', { name: /post/i }))
  expect(await screen.findByText(/title is required/i)).toBeInTheDocument()
})
\end{lstlisting}

\subsection*{API (Express + supertest)}
\begin{lstlisting}
import request from 'supertest'
import app from '../functions/app'

test('TC-007: blocks job create when kyc not verified', async () => {
  const token = await getAuthToken({ kycVerified: false })
  const res = await request(app)
    .post('/jobs')
    .set('Authorization', `Bearer ${token}`)
    .send({ title: 'Yard help', ... })
  expect(res.status).toBe(403)
})
\end{lstlisting}

\subsection*{Firestore Rules (rules-unit-testing)}
\begin{lstlisting}
it('TC-012: rejects write without kycVerified', async () => {
  const db = authedDB({ uid: 'u1', kycVerified: false })
  const ref = db.collection('jobs').doc('j1')
  await assertFails(ref.set({ title: 'T', ... }))
})
\end{lstlisting}

\end{document}
